### 2025-02-14 README.Rmd
update README

[main.zip](/archive/refs/heads/main.zip).

@@

1. Open the folder in your preferred IDE
2. run `renv::restore()` to install the required R packages
3. run `quarto::quarto_render("analysis/paper/paper.qmd", output_format = "pdf")` in the R console (requires installing **quarto** R package) or `quarto render analysis/paper/paper.qmd --to pdf` to produce a PDF
4. find the pdf in `./analysis/paper/_output`

>>>>

[main.zip](https://github.com/bbartholdy/mb11CalculusPilot/archive/refs/heads/main.zip)

@@

1. open the folder in your preferred IDE
2. run `renv::restore()` to install the required R packages
3. run `quarto::quarto_render("analysis/paper/paper.qmd", output_format = "html")` in the R console (requires installing **quarto** R package) or `quarto render analysis/paper/paper.qmd --to html` to produce an HTML
4. open the output `./analysis/paper/_output/version-of-record.html` in a browser
